---
title: "Scrapping data from twitter with twitter api v2"
author: "birasafab"
date: "3/2/2022"
output: html_document
editor_options: 
  chunk_output_type: console
---

# Setting up your environment variable

For the code examples, I’m going to be showing today, you will want to create an environment variable for your bearer token. The Bearer Token is what allows you to authenticate to the Twitter API and start making requests. First, replace “your-bearer-token” with your own bearer token, which can be obtained from the keys and tokens section of your App in the developer portal. You’ll need to run this line of code in the console before you start writing a script.

```{r}
Sys.setenv(BEARER_TOKEN = "AAAAAAAAAAAAAAAAAAAAANhJZwEAAAAArPN7hQWHU%2F9M%2B1qC5awBy%2BG3S5E%3DCTGxpeoDj3TcHm02cBPAyBaV2IsGqklDvvL13SuVh0f8cw1GD4")
```

# Making your request

```{r}
require(httr)
require(jsonlite)
require(dplyr)
```


The first step in your code sample is to get set up to authenticate to the Twitter API. Grab the Bearer Token you pulled from your App, and pass that into your headers for authentication. In the below example, replace $BEARER_TOKEN with your token. 

```{r}

bearer_token <- Sys.getenv("AAAAAAAAAAAAAAAAAAAAANhJZwEAAAAArPN7hQWHU%2F9M%2B1qC5awBy%2BG3S5E%3DCTGxpeoDj3TcHm02cBPAyBaV2IsGqklDvvL13SuVh0f8cw1GD4")


headers <- c(`Authorization` = sprintf('Bearer %s', bearer_token))
```



```{r}
params <- list(`user.fields` = 'description',
               `expansion` = 'pinned_tweet_id')
```


```{r}
# handle <- readline('@BIRASAFABRICE')

url_handle <-   sprintf('https://api.twitter.com/2/users/by?usernames=%s', "@Bnyirimana")
```


```{r}
response <-  httr::GET(url = url_handle,
            httr::add_headers(.headers = headers),
            query = params)
obj <- httr::content(response, as = "text")
print(obj)
```

```{r}
json_data <- fromJSON(obj, flatten = TRUE) %>% as.data.frame
View(json_data)
```



```{r}
final <-
  sprintf(
    "Handle: %s\nBio: %s\nPinned Tweet: %s",
    json_data$data.username,
    json_data$data.description,
    json_data$includes.tweets.text
  )
```



# Using rtweet package

```{r}
library(rtweet)

# downloading twitter data of interest (related to #Rstats)

tweets_kayembe <- search_tweets(
  "#KayembeMustResign", retryonratelimit = TRUE
)


rtweets_kayembe <- search_tweets(
  "#KayembeMustResign", retryonratelimit = TRUE, n= 30000
)

# saving the downloaded data

# write.csv(x=rt, file = "~Downloads/rstats_hash_downloads.csv")

```


# Reading the saved data
```{r}
tweets  = read.csv(file = "tweets.csv") %>% 
  tibble()

tweets %>%
  count(user_id, screen_name, sort = TRUE) %>% 
  View()


```


# Posting my first tweet
```{r}

## plot time series of tweets
ts_plot(rt, "3 hours") +
  ggplot2::theme_minimal() +
  ggplot2::theme(plot.title = ggplot2::element_text(face = "bold")) +
  ggplot2::labs(
    x = NULL, y = NULL,
    title = "Frequency of #rstats Twitter statuses from past 9 days",
    subtitle = "Twitter status (tweet) counts aggregated using three-hour intervals",
    caption = "\n By Nyirimana Source: Data collected from Twitter's REST API via rtweet"
  )

ggsave(filename = "tweetter's data.png", device = "png")

post_tweet(status = "My first tweet while using #rtweet package, #rstats, #data #scrapping #dataviz #66daysofdata #100daysofcode",
           media = "tweetter's data.png")
```

## Get friends list of user with the handle "1234
```{r}
friends = get_friends(as_screenname(c("1234","BIRASAFABRICE")))
```


```{r}
users <- c("birasafabrice","bnyirimana", "patbirasa", "cnn")

famous_tweeters <- lookup_users(users)

## preview users data
famous_tweeters %>% 
  View()
```


# get trends in my location
```{r}
sf <- get_trends("san francisco")


writexl::write_xlsx(birasa_liked,path = "birasa_liked_tweets.xlsx")
```


# Get trends in Rwanda
```{r}
Rwanda = get_trends(-1.932323,30.047462)



which = get_trends(c(30.047462,-1.932323))



Kenya_trending = get_trends(woeid = 1528488)

which %>% 
  View()
```

# accessing my 1,000 most recent favorited statuses (liked tweets)
```{r}
birasa_liked = get_favorites("birasafabrice", n = 300)
```
