---
title: "trends in Rwanda from twitter"
author: "birasafab"
date: "4/22/2022"
output: html_document
---

# Setting up your environment variable

For the code examples, I’m going to be showing today, you will want to create an environment variable for your bearer token. The Bearer Token is what allows you to authenticate to the Twitter API and start making requests. First, replace “your-bearer-token” with your own bearer token, which can be obtained from the keys and tokens section of your App in the developer portal. You’ll need to run this line of code in the console before you start writing a script.

```{r}
Sys.setenv(BEARER_TOKEN = "AAAAAAAAAAAAAAAAAAAAANhJZwEAAAAArPN7hQWHU%2F9M%2B1qC5awBy%2BG3S5E%3DCTGxpeoDj3TcHm02cBPAyBaV2IsGqklDvvL13SuVh0f8cw1GD4")
```

# Making your request

```{r}
require(httr)
require(jsonlite)
require(dplyr)
```


The first step in your code sample is to get set up to authenticate to the Twitter API. Grab the Bearer Token you pulled from your App, and pass that into your headers for authentication. In the below example, replace $BEARER_TOKEN with your token. 

```{r}

bearer_token <- Sys.getenv("AAAAAAAAAAAAAAAAAAAAANhJZwEAAAAArPN7hQWHU%2F9M%2B1qC5awBy%2BG3S5E%3DCTGxpeoDj3TcHm02cBPAyBaV2IsGqklDvvL13SuVh0f8cw1GD4")


headers <- c(`Authorization` = sprintf('Bearer %s', bearer_token))
```



```{r}
params <- list(`user.fields` = 'description',
               `expansion` = 'pinned_tweet_id')
```


```{r}
# handle <- readline('@BIRASAFABRICE')

url_handle <-   sprintf('https://api.twitter.com/2/users/by?usernames=%s', "@Bnyirimana")
```


```{r}
response <-  httr::GET(url = url_handle,
            httr::add_headers(.headers = headers),
            query = params)
obj <- httr::content(response, as = "text")
print(obj)
```

```{r}
json_data <- fromJSON(obj, flatten = TRUE) %>% as.data.frame
View(json_data)
```



```{r}
final <-
  sprintf(
    "Handle: %s\nBio: %s\nPinned Tweet: %s",
    json_data$data.username,
    json_data$data.description,
    json_data$includes.tweets.text
  )
```



# Using rtweet package

```{r}
library(rtweet)

# downloading twitter data of interest (related to #Rstats)

tweets_kayembe <- search_tweets(
  "#KayembeMustResign", retryonratelimit = TRUE
)


rtweets_kayembe <- search_tweets(
  "#KayembeMustResign", retryonratelimit = TRUE, n= 30000
)

# saving the downloaded data

# write.csv(x=rt, file = "~Downloads/rstats_hash_downloads.csv")

```