---
title: "Erasmus program Europe"
author: "birasafab"
date: "3/15/2022"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse, quietly = TRUE)
```

# Loading this week dataset
```{r}
erasmus <- read.csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2022/2022-03-08/erasmus.csv') %>% 
  tibble()
```

# cleaning the loaded dataset
```{r}
# Loading the the package for dealing with dates

library(lubridate)   # loading the package for dealing with date related data
library(countrycode) # loading the package for translation of country codes


# cleaning the dataset for dates to be used
erasmus = erasmus %>% 
  mutate(date = lubridate::ym(mobility_start_month),
         month = month(date)) %>% 
  filter(participant_gender != "Undefined") %>% 
  # cleaning country codes that were mistakenly recorded to match countrycode requirements
  mutate(
    sending_country_code = ifelse(sending_country_code=="UK","GB",sending_country_code),
    sending_country_code = ifelse(sending_country_code=="EL","GR",sending_country_code),
        receiving_country_code = ifelse(receiving_country_code=="UK","GB",receiving_country_code),
    receiving_country_code = ifelse(receiving_country_code=="EL","GR",receiving_country_code)
  ) %>% 
  
  # adding the country names by referring to countrycode (iso2) as cleaned above
  mutate(
    sending_country = countrycode(sending_country_code, origin = "iso2c" , destination = 'country.name'),
    receiving_country = countrycode(receiving_country_code, origin = "iso2c" , destination = 'country.name')
  )
```

* Is it real that ZW stands for Zimbabwe among participant_nationality? 
to be well checked.
* What is the meaning of the participant country in relationship with receiving- and sending-countries?


# visualizing how participation by gender has variated on monthly basis
```{r}
erasmus %>% 
  group_by(month) %>% 
  count(participant_gender) %>% 
  ungroup() %>% 
  ggplot(aes(month,n, fill = participant_gender))+
  geom_line()+
  geom_label(aes(label = paste(month,n, sep = ",")))+
  labs(y = "# of participants by gender",
       x = "month of observation",
       title = "Number of ERASMUS participants per month since 2014 up to 2020")+
  theme_light()+
  theme(
    legend.position = "top"
  )
```


```{r}
erasmus  %>% 
  select(sending_country_code, sending_country,receiving_country_code, receiving_country, participant_nationality) %>% 
  View()
```

# checking how factor/character variables behave in plots
```{r}
month = c("jan","feb","mar","apr","may","jun","jul","aug","sep","oct","nov","dec")
counts = c(8903,12971,15061,16071,17517,12644,8251,6702,15104,20019,20344,10467)


factor(month, levels=c("jan","feb","mar","apr","may","jun","jul","aug","sep","oct","nov","dec"))


new = tibble(month,counts)


new %>% 
  ggplot(aes(month, counts))+
  geom_col()
```

* In fact, factor variable aren't easily plotted with linear graph, this topic is to be further researched on for advanced knowledge.

# Creating ggsankey diagram

* The following code have been used to create ggsankey diagram
```{r}
# loading the required package for ggsankey
library(ggsankey)

# Indicators for making ggsankey diagram

new_erasmus = erasmus %>%
 # filter(sending_country %in% c("Germany","Poland","United Kingdom","Spain")) %>%
  make_long(sending_country,participant_gender, receiving_country)

new_erasmus %>%
  ggplot(aes(x = x, node = node, next_x = next_x,next_node = next_node,fill = factor(node)))+
  geom_sankey(flow.alpha = .5,
              show.legend = FALSE,
              width = .01,
              na.rm = TRUE,
 #             type = "alluvial",
              smooth = 25)+
 theme_light()+
  labs(
    caption = "Plot by Birasafab"
  )+
  theme(
      panel.grid = element_blank(),
      axis.text = element_blank(),
      panel.background = element_rect(fill = "#f4f1ac"),
      axis.ticks = element_blank(),
      axis.title = element_blank(),
 panel.border = element_blank(),
 plot.background = element_rect(fill = "black"),
 plot.caption = element_text(color = "white", size = 13, face = "italic")
    )+
  geom_label(y=1,x=1, aes(label = "birasa"))
```



