---
title: "TidyTemplate"
date: 2022-09-28
output: html_document
editor_options: 
  chunk_output_type: console
---

# Analysing LEGO dataset

This work has been created with reference to the live screencast from Drob.

I have manually downloaded the datasets to be used along with this video. from this [link](https://rebrickable.com/downloads/).

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(tidytuesdayR)
library(scales)
theme_set(theme_light())

```

```{r}
# downloading the the datasets of interest while using the conventional package code

tt = tt_load("2022-09-06")
```
* Downloading by using the conventional code doesn't work, therefore I had to download the same datasets by using my download from the above linked website.

```{r}
# Reading the downloaded datasets

lego_files <- tibble(file = dir("C:/Users/fabrice.birasa/Documents/My files/Learning/R learning/Tidytuesday2022/legos", full.names = TRUE))%>% 
  mutate(data = map(file,read_csv)) %>% 
  extract(file,"name","legos/(.*).csv.gz") %>% 
  # Have used deframe to convert the dataframe just created into a named vector or a list.
  deframe()
```

```{r}
#creating a histogram for sets
sets = lego_files$sets 


sets%>% 
  ggplot()+
  geom_histogram(aes(year))

#finding the geom_column graph for the same sets data

sets %>% 
  count(year) %>% 
  ggplot(aes(year,n))+
  geom_col()+
  labs(x = "Year",y = "# of LEGO Sets")
```

### summarizing the common LEGO sets
```{r}
sets %>% 
  group_by(name) %>% 
  summarise(n_sets = n(),
            year_first = min(year),
            year_last = max(year)) %>% 
  arrange(desc(n_sets))

```

* Joining both sets dataset and the theme ones
```{r}
themes = lego_files$themes

sets_with_themes = sets %>% 
  left_join(themes %>% 
              select(id,theme_name = name),by = c(theme_id = "id")) %>%
  mutate(num_parts = na_if(num_parts,0))


sets_with_themes%>% 
  count(theme_name,sort = TRUE) %>% 
  #mutate(theme_name = fct_lump(theme_name,5)) %>% 
  head(25) %>% 
  mutate(theme_name = fct_reorder(theme_name,n)) %>% 
  ggplot(aes(n,theme_name))+
  geom_col()+
  labs(
    title = "MOst Common LEGO Themes",
    x = "# of sets",
    y = ""
  )
```

```{r}
sets_with_themes %>% 
  group_by(theme_name) %>% 
  summarise(n_sets = n(),
            median_parts = median(num_parts, na.rm = TRUE)) %>% 
  arrange(desc(n_sets))
```

