---
title: "Learning with David Robinson on Tidytuesday"
date: 2022-02-25
output: html_document
---

# Loading the required packages

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(tidytuesdayR)

```

# Load this week's data
```{r Load}

# either of the below method will load this week's dataset

tt = tt_load("2022-02-22")

freedom = tt$freedom
 freedom <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2022/2022-02-22/freedom.csv')

```


# Data cleaning
```{r}
freedom = freedom %>% 
  janitor::clean_names() %>% 
  mutate(country_new = str_replace_all(country,"(.+Ivoire)$","Cote d'Ivoire")) %>% 
  rename(political_rights = pr,
         civil_liberties = cl)

freedom %>% 
  count(year)
  arrange(desc(year))
```

* period: 1995 - 2020
* observations: 193 countries observation in the above period (there are some missing values in earlier years)


# visualizing individual country data
```{r}
# Histogram of civil liberties

freedom %>% 
  ggplot(aes(civil_liberties))+
  geom_histogram()+
  facet_wrap(~region_name, ncol = 1,strip.position = "right")



freedom %>% 
  filter(country == "United States of America") %>% 
  ggplot(aes(year, civil_liberties))+
  geom_col()+
  expand_limits(y = c(0,2))
```

Civil Liberties is a scale of 1 to 7


## Looking for just 2020 year
```{r}
by_region = freedom %>% 
  filter(year == 2020) %>% 
  group_by(region_name) %>% 
  summarise(
    n_countries = n(),
    avg_political_parties = mean(political_rights),
    avg_civil_liberties = mean(civil_liberties)
  ) 

by_region %>% 
  ggplot(aes(avg_civil_liberties,avg_political_parties))+
  geom_point(aes(size = n_countries))+
  geom_abline(color = "red")+
  expand_limits(x=0,y=0, size = 0)+
  geom_text(aes(label = region_name), hjust = 1.2, vjust = 1.2)+
  labs(
    title = "Relationship between political parties and civil liberties",
    subtitle = "There's a strong positive correlation between political rights and civil liberties"
  )+
  theme_classic()+
  ggrepel::geom_label_repel(aes(label = region_name), fill = "black",color = "#ff33ff",nudge_x = 2, nudge_y = -1)
```

As per the above plot, Civil_liberties and Polities parties variables are highly correlated


```{r}

freedom %>% 
  ggplot(aes(political_rights,civil_liberties))+
         geom_jitter()+
#  geom_text(aes(label = region_name))+
  geom_abline(color = "red")+
  expand_limits(y = 0, x = 0)+
  labs(
    title = "Correlation between civil_liberties and political_rights",
    subtitle = "there is a strong correlation between Civil liberties and political rights",
    x = "# Political rights",
    y = "# Civil liberties"
  )+
  theme_light()
```

# comparing civil liberties vs political parties per continent
```{r}
freedom %>% 
#  filter(year == 2020) %>% 
  pivot_longer(cols = c(civil_liberties,political_rights), values_to = "value", names_to = "metric") %>% 
  mutate(metric = str_to_title(str_replace(metric,"_"," "))) %>% 
  mutate(region_name = fct_reorder(region_name,value)) %>% 
  count(region_name,metric,year,value) %>% 
  ggplot(aes(value,n))+
  geom_col()+
  facet_grid(region_name~metric)+
# the following commented code will not function within this PC, because I am not logged in as administrator of the PC  
 # gganimate::transition_manual(year)+
  
  labs(
    x = "World Freedom Index rating",
    y = "# countries",
    title = "Distribution of World Freedom Index per region (Continent)"
  )+
  theme_grey()+
    theme(
      plot.background = element_rect(fill = "grey"),
      strip.background = element_rect(fill = "black"),
      strip.text = element_text(color = "white")
    )
  
```


# Importing World bank data to find the relationship of freedom in world vs status of economic development

## The following plot 
```{r}
library(tidyverse)
library(WDI)
library(scales)

wordl_gpd_ppp = WDI(indicator = "	
NY.GDP.MKTP.PP.CD") %>% 
  tibble()

wordl_gpd_ppp %>%
  janitor::clean_names() %>% 
  ggplot(aes(ny_gdp_mktp_pp_cd, year, color = country))+
  geom_jitter(size = 10)+
  scale_x_continuous(label = comma)+
  ylim(c(1990,2021))+
  xlim(c(0,5000000000000))+
  geom_label(x=  4590000000000, y = 2021, aes(label = "by Birasafab"), size = 4, fill = "yellow")+
  theme_void( )+
  theme(
    legend.position = "none",
    panel.background = element_rect(fill = "black")
  )

```
